Hochschild cohomology of torus-equivariant D-modules

### 2017-05-30 paper.tex
More small changes.

[subvariety <-> subscheme]
[macros]
[-advisor]
[map in contraction principle]

@@

\subsection*{Acknowledgments}
I would like to thank my advisor, David Nadler, for the original motivation for this project and many discussions concerning it.

@@

\begin{Thm}[{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
    \label{thm:pre:contraction_principle}%
    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
    Then there is an isomorphism of functors
    \[
        i^* \cong π_* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}.
    \]
\end{Thm}

@@

Finally, it will be useful to consider only partial compactifications.
That is, in the constructions of Section~\ref{sec:base-change:compactification}, instead of going all the way to $\bar G$ we only some subvariety of it.
Thus let $H$ be a $G×G$-stable subvariety of $\bar G$ containing $G$, and let $^H\bar{Γ}$ be the closure of $Γ$ in $H × X × X$.
We set
\[
    ^H\bar{\stack X} = \rquot{^H\bar{Γ}}{G×G}.
\]
Clearly, if $\left\{H_i\right\}$ is an open cover of $\bar G$ by $G×G$-stable subvarieties (each containing $G$), then $\left\{{}^{H_i}\bar{\stack X}\right\}$ is an open cover of $\bar{\stack X}$.

@@

    We will do so by using the Contraction Principle of Theorem~\ref{thm:pre:contraction_principle}.
    For this we will introducing a contractive $\Gm$-action on $\bar Γ$ and all $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ such that the morphisms
    \begin{equation}
        \label{eq:torus:middle_row}
        \begin{tikzcd}
            \bar Γ^{S₁,S₂} &
            \stabcls{S₁,S₂}{\stack X} \arrow[l, "\bar p₂"'] &
            \stabclsY[\stack Y₁]{S₁,S₂}{\stack X} \arrow[l, "\scls{h₁}"'] &
            \stabclsY[\stack Y₂]{S₁,S₂}{\stack X} \arrow[l, "\scls{f}"']
        \end{tikzcd}
    \end{equation}
    are $\Gm$-equivariant (where we abuse notation to denote the restrictions of the morphisms with the same name).

>>>>

[macros]

@@

\subsection*{Acknowledgments}
I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.

@@

\begin{Thm}[{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
    \label{thm:pre:contraction_principle}%
    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
    Then there is a canonical isomorphism of functors
    \[
        π_* \cong i^* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}
    \]
    given by adjunction
    \[
        π_* → π_* i_* i^* = (π ∘ i)_* i^* = i^*.
    \]
\end{Thm}

@@

Finally, it will be useful to consider only partial compactifications.
That is, in the constructions of Section~\ref{sec:base-change:compactification}, instead of going all the way to $\bar G$ we only use some subvariety of it.
Thus let $H$ be a $G×G$-stable subvariety of $\bar G$ containing $G$, and let $^H\bar{Γ}$ be the closure of $Γ$ in $H × X × X$.
We set
\[
    ^H\bar{\stack X} = \rquot{^H\bar{Γ}}{G×G}.
\]
Clearly, if $\left\{H_i\right\}$ is an open cover of $\bar G$ by $G×G$-stable subvarieties (each containing $G$), then $\left\{{}^{H_i}\bar{\stack X}\right\}$ is an open cover of $\bar{\stack X}$.

@@

    We will do so by using the contraction principle of Theorem~\ref{thm:pre:contraction_principle}.
    For this we will introducing a contractive $\Gm$-action on $\bar Γ$ and all $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ such that the morphisms
    \begin{equation}
        \label{eq:torus:middle_row}
        \begin{tikzcd}
            \bar Γ^{S₁,S₂} &
            \stabcls{S₁,S₂}{\stack X} \arrow[l, "\bar p₂"'] &
            \stabclsY[\stack Y₁]{S₁,S₂}{\stack X} \arrow[l, "\scls{h₁}"'] &
            \stabclsY[\stack Y₂]{S₁,S₂}{\stack X} \arrow[l, "\scls{f}"']
        \end{tikzcd}
    \end{equation}
    are $\Gm$-equivariant (where we abuse notation to denote the restrictions of the morphisms with the same name).
